How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-13 Paper/paper.tex
Additions to related work

>>>>

Large-scale analyses of Scratch projects have been made using the dataset made available by the Lifelong Kindergarten Group at the MIT Media Lab, which contains data for Scratch projects created until 2012, when the web-based programming environment was introduced. In \cite{yang_2015}, this dataset was used for exploring the learning patterns of users in terms of block use over their first 50 projects. Dasgupta \emph{et al.} investigated how project remixing relates to the adoption of computational thinking concepts \cite{Dasgupta_2016}. In \cite{fields_2014}, the use of programming concepts was examined in relation to the level of participation (commenting, remixing, etc), the gender, and the account age of 5,000 Scratch programmers.
